The Bug Catalog of the Maven Ecosystem

### 2014-02-16 docs/msr.tex
added corrplot in the text.
analysing data structure (initial)

\section{Tools and Findings}
\label{sec:find}

As we mentioned earlier our data was stored in a
Mongo{\sc db} database. Hence, it is easy to either create
queries to find out basic information like:
``how many bad practice bugs exist in the repository", or
create scripts that can help us capture correlations
that could provide valuable findings.
Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository.

@@

>>>>

\section{Data and Findings}
\label{sec:find}

As we mentioned earlier our data was stored in a
Mongo{\sc db} database, thus all the data stored 
converted to the {\sc json} format. Originally, FindBugs output is in {\sc xml}, the conversion was a straight forward mapping
of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a header metadata section, which contained
several additional information regarding the jar file that has been processed.
% dimitro@bkarak: add content here.
Hence, it is easy to either create
queries to find out basic information like:
``how many bad practice bugs exist in the repository", or
create scripts that can help us capture correlations
that could provide valuable findings.
Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.43]{corrplot.pdf}
  \caption{Correlation matrix plot for bug categories.}
  \label{fig:corrplot}
\end{figure}
